%%%%
% MTecknology's Resume
%%%%
% Author: Michael Lustfield
% License: CC-BY-4
% - https://creativecommons.org/licenses/by/4.0/legalcode.txt
%%%%

\documentclass[letterpaper,10pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
%% NOTE: Everything between here and END_FILE can
%% be relocated to "mteck.sty" and then included with:
%\usepackage{mteck}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Sans-Serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
% Use with \color{Name}
% Can wrap entire heading with {\color{accent} [...] }
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
% Usage: \documentTitle{Name}{Details}
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    %{\footnotesize\color{accentTitle} #2}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

% Create a footer with correct padding
% Usage: \documentFooter{\thepage of X}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
% Usage: \numberedPages
% WARNING: Must run pdflatex twice!
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
% Usage: \section{Title}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
% Usage: \tinysection{Title}
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
% Usage: \heading{Left}{Right}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
% Usage: \begin{resume_list} [items] \end{resume_list}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
  %\vspace{-2pt}
}

% Formats an item to use as an itemized title
% Usage: \itemTitle{Title}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

% Bullets used in itemized lists
\renewcommand\labelitemi{--}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%


%===================%
% John Doe's Resume %
%===================%

%\numberedPages % NOTE: lastpage requires a second build
%\documentFooter{\thepage of 2} % Does similar without using lastpage
\begin{document}

  %---------%
  % Heading %
  %---------%

  \documentTitle{Asaduzzaman Noor}{
    % Web Version
    %\raisebox{-0.05\height} \faPhone\ [redacted - web copy] ~
    %\raisebox{-0.15\height} \faEnvelope\ [redacted - web copy] ~
    %%
    \href{tel:+8801756214236}{
      \raisebox{-0.05\height} \faPhone\ +880 17 56 214 236} ~ | ~
    \href{mailto:asad.noor.antor@gmail.com}{
      \raisebox{-0.15\height} \faEnvelope\ asad.noor.antor@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/asd-noor/}{
      \raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/asd-noor} ~ | ~
    \href{https://github.com/asd-noor}{
      \raisebox{-0.15\height} \faGithub\ github.com/asd-noor}
  }

  %---------%
  % Summary %
  %---------%

  % \tinysection{Summary}
  \begin{center}
  \emph{Engineer crafting high-performance systems with automation — where efficiency meets intelligent design.}
  \end{center}

  \section{Brief}

I’m a Backend Engineer who thrives on building lean, high-performance distributed systems. While I can navigate the frontend when needed, my real passion lies deep in system programming and Linux internals. With hands-on experience in Go, Kubernetes, AWS, GCP, and scalable architectures, I focus on crafting resilient, efficient solutions and automating everything possible. Lately, I’ve been diving into Machine Learning—exploring, using, and even building AI tools that push the limits of intelligent automation.

  %--------%
  % Skills %
  %--------%

  \section{Skills}

  \begin{multicols}{2}
    \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=75pt]
      \item[\textbf{Languages}] Go, Python, JavaScript, Zig, Bash
      \item[\textbf{Frameworks}] Echo, React, TailwindCSS. Templ (Go)
      \item[\textbf{Databases}] PostgreSQL, Redis/KeyDB, DynamoDB, Elasticsearch, InfluxDB
      \item[\textbf{Message Brokers}] Asynq (Go), NATS
      \item[\textbf{Infrastructure}] Kubernetes, Docker, Pulumi/Terraform, Linux
      \item[\textbf{Observability}] Grafana, Prometheus, Loki
      \item[\textbf{Cloud Platform}] AWS, GCP
    \end{itemize}
  \end{multicols}

  %------------%
  % Experience %
  %------------%

  \section{Experience}

  \headingBf{Vivasoft Limited}{Aug 2022 -- Present}
  \headingIt{Software Engineer}{}
  % \vspace{5pt}
  \begin{resume_list}
    \itemTitle{\textit{\textcolor{blue}{\href{https://klikit.io}{Klikit}}}}
    \item Microservice to handle uploading files to GCS, as well as image conversion and resizing.
    \item Microservice to send emails with MailGun.
    \item Microservice to send SMS and WhatsApp messages to users.
    \item Integrate Third-Party Platform to Klikit.
    \item Collaborated with other microservices as necessary.
    \item \textit{Tech Stack: Go, MySQL, Docker, Kubernetes, AWS EKS, GCP GCS, MailGun}

   % \vspace{5pt}
    
    \itemTitle{\textit{\textcolor{blue}{\href{https://hink.me}{Hink}}}}
    \item Refactored the project with Clean Architecture principle.
    \item Fixed bugs.
    \item Deployed a lambda for handling media post-processing.
    \item \textit{Tech Stack: Go, MySQL, Elasticsearch, Docker, Kubernetes, AWS S3, GCP GKE, Google Maps API}
    
    % \vspace{5pt}
    
    \itemTitle{\textit{\textcolor{blue}{\href{https://apps.apple.com/us/app/circle-socials/id6476143567}{Circle}}}}
    \item Refactored DynamoDB table design for better indexing and faster data retrieval as well as reducing read/write costs.
    \item Improved user feed.
    \item Automated place registrations from user pings.
    \item User management features for admin.
    \item \textit{Tech Stack: Go, AWS DynamoDB, Docker Swarm, AWS EC2, AWS SES, Google Maps API}

    \vspace{5pt}

    \itemTitle{\textit{GPS Server (Part of backend for Sister Concerns)}}
    \item Redesigned the software architecture to an more efficient version. (R\&D)
    \item Improved DB Design.
    \item Added real-time tracking and analytics.
    \item \textit{Tech Stack: Go, PostgreSQL (TimescaleDB), Redis}

    \vspace{5pt}
    
    \itemTitle{\textit{Anonymous Feedback System}}
    \item Designed and implemented a secure feedback system with \textbf{untraceable} Google login.
    \item Designed UI and Portal, segregated by user type.
    \item \textit{Tech Stack: Go, PostgreSQL, JavaScript (React)}

    \vspace{5pt}
    
    \itemTitle{\textit{Mock Server}}
    \item Designed and implemented a multi-tenant mock server which enables live HTTP request for Frontend teams until the Backend is ready.
    \item \textit{Tech Stack: Go, PostgreSQL, JavaScript (React)}

    \vspace{5pt}
    
    \itemTitle{\textit{SIP Server}}
    \item Designed and implemented a horizontally scalable SIP Server for Telecommunication System.
    \item Added geo-restrictions, rate limiting.
    \item Added Monitoring and Analytics for calls and server.
    \item Added voice mail and email notification support.
    \item \textit{Tech Stack: Asterisk, OpenSIPS, RTPEngine, PostFix Relay, MySQL, PostgreSQL, Traefik, Kubernetes}
  \end{resume_list}

  \vspace{10pt}

  \headingBf{Softimist (Part-time, in weekends)}{Sep 2025 -- Present}
  \headingIt{Software Engineer}{}
  % \vspace{5pt}
  \begin{resume_list}
    \itemTitle{Edushade (Learning Management System)}
    \item Designed and implemented File Manager for LMS.
    \item Designed and implemented billing service with SSLCommerz as the gateway.
    \item Enabled one-time purchase, EMI purchase and susbscription system.
    \item \textit{Tech Stack: Go, PostgreSQL, Redis, SSLCommerz}
  \end{resume_list}

  \vspace{10pt}


  %-----------%
  % Education %
  %-----------%

  \section{Education}

  \headingBf{North South University, BD}{2021} % Note: Adding year(s) exposes an implied age
  \headingIt{Bachelor of Science in Computer Science and Engineering}{}
  
  % \headingBf{Certifications}{}
  % \begin{resume_list}
  %  \item Salt \hspace{2pt}- SaltStack Certified Engineer
  %  \item GCP - Professional Cloud Architect
  % \end{resume_list}

  %----------------------------%
  % Extracurricular Activities %
  %----------------------------%

  \vspace{5pt}

  \section{Publications}
  \begin{resume_list}
      \item Patch-Wise Semantic Segmentation of Sedimentation from High-Resolution Satellite Images Using Deep Learning --- \textcolor{blue}{\emph{\href{https://link.springer.com/chapter/10.1007/978-3-030-85030-2_41}{Springer - 2021}}} 
      \item Effect of Label Noise on Multi-Class Semantic Segmentation: A Case Study on Bangladesh Marine Region --- \textcolor{blue}{\emph{\href{https://www.tandfonline.com/doi/full/10.1080/08839514.2022.2039348}{Taylor \& Francis - 2022}}} 
  \end{resume_list}

  \vspace{5pt}

  \section{Awards}
  \begin{resume_list}
    \item President's Scout Award (2011)
    \item IELTS, Band 7.5 (2016)
  \end{resume_list}

  \vspace{5pt}

  \section{Projects}

  \headingBf{Inventory Management \& Ledger \textit{(Personal Paid Project)}}{Jan 2022}
  \begin{resume_list}
    \item Desktop App: built with Rust (Tauri), ReactJS, SQLite 
  \end{resume_list}

  \headingBf{Local Memory Agent for universal LLMs}{Oct 2025}
  \begin{resume_list}
    \item MCP Server: Provides tools for efficiently storing and retrieving general memory, project context for AI tools.
    \item \textit{Tech Stack: Python (Pydantic AI, MemVid)}
  \end{resume_list}

\end{document}

